Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-06-10 Manuscript/main.tex
Updated commodity claims list

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 202.1, df = 100, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
Similarly, the initial seed field pSEM also had several missing paths (C = 37.54, df = 56, p = 0.027), which we corrected (C = 58.10, df = 64, p = 0.68).
Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.

>>>>

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified for the initial commodity model (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM that included missing paths was adequate (C = 81.6, df = 86, p = 0.62).
Similarly, the initial seed field pSEM also had several missing paths (C = 37.54, df = 56, p = 0.027), which we corrected (C = 58.10, df = 64, p = 0.68).
Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.
